---
title: "MA678 Final Project"
author: "Yin Xu"
date: "2022-11-30"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(ggplot2)
library(lme4)
library(Matrix)
library(pbkrtest)
```

## Abstract
In most universities, AI, Statistics and Data Science are some of the most popular majors, plenty of students choose these majors since if they have the AI/ML and Big Data background, they may find jobs easily after university. According to this point, there is a dataset from ai-jobs shows that the titles, locations and other variables which effect the salaries. The report includes 4 main parts: introduction, method, result and discussion.

## Introduction
As we always know, the job titles, locations of companies, salary currency and other factors influence the amount of a person's salary. However, after COVID-19 came into everyone's life, some of jobs became remote to avoid direct contact, therefore, remote jobs may become one factor which influence the salaries. Besides, some


```{r}
salaries_all <- read.csv("salaries.csv")
salaries <- subset(salaries_all, work_year == 2022)
salaries_ft <- subset(salaries, employment_type == "FT")
salaries_ft_usd <- subset(salaries_ft, salary_currency == "USD")
```













































